Concurrent Programming with Harmony

### 2020-07-30 book/paper.tex
Latest

    for a lock to become available.}

@@

      application-defined condition}

@@

  description={is a property that two processes never enter the same critical section}

@@

      between processes and threads.  A process has a program counter, a register,
      and a stack}

@@

    submit items and one or more consuming process want to receive them.  No item

>>>>

    for a lock to become available}

@@

      application-defined condition instead of blocking}

@@

  description={is the property that two processes never enter the same critical section}

@@

      between processes and threads.  A process has a current context and
      updates its context every time it executes a machine instruction}

@@

    submit items and one or more consuming processes want to receive them.  No item
